IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2015-01-07 paper/abstract.tex
reviewer 1 grammar/spelling

\begin{abstract}
Many important security problems in JavaScript, such as browser
extension security, untrusted JavaScript libraries and safe
integration of mutually distrustful websites (mash-ups), may be
effectively addressed using an efficient implementation of information
flow control (IFC).  Unfortunately existing fine-grained approaches to
JavaScript IFC require modifications to the language semantics and its engine, a
non-goal for browser applications.  In this work, we take the ideas of
coarse-grained dynamic IFC and provide the theoretical
foundation for a language-based approach that can be applied to any
programming language for which external effects can be controlled.  We
then apply this formalism to JavaScript, in the context of Node.js and
Firefox, and show how it generalizes to the C programmings language.  Our methodology offers
design principles for the construction of information flow control
systems when isolation can easily be achieved, as well as
compositional proofs for optimized concrete implementations of these
systems, by relating them to their isolated variants.
\end{abstract}

>>>>

\begin{abstract}
Many important security problems in JavaScript, such as browser
extension security, untrusted JavaScript libraries and safe
integration of mutually distrustful websites (mash-ups), may be
effectively addressed using an efficient implementation of information
flow control (IFC).  Unfortunately existing fine-grained approaches to
JavaScript IFC require modifications to the language semantics and its engine, a
non-goal for browser applications.  In this work, we take the ideas of
coarse-grained dynamic IFC and provide the theoretical
foundation for a language-based approach that can be applied to any
programming language for which external effects can be controlled.  We
then apply this formalism to server- and client-side JavaScript,
show how it generalizes to the C programming language, and connect it
to the Haskell LIO system.  Our methodology offers
design principles for the construction of information flow control
systems when isolation can easily be achieved, as well as
compositional proofs for optimized concrete implementations of these
systems, by relating them to their isolated variants.
\end{abstract}

### 2015-01-07 paper/conclusion.tex
reviewer 1 grammar/spelling

In this paper, we argued that when designing a coarse-grained IFC
system, it is better to start with a fully isolated, multi-task system
and work one's way back to the model of a single language equipped
with IFC.  We showed
how to prove systems designed this way can be proved non-interferent
without needing to rely on details of the target language, and
we provided conditions on how to securely refine our formal semantics to
consider optimizations required in practice.  We connected our semantics
to two IFC implementations for JavaScript based on this formalism,
explained how our methodology improved an exiting IFC system for Haskell,
and proposed
an IFC system for C using hardware isolation.
By systematically applying ideas from IFC in operating systems to programming languages,
we hope to have elucidated some of the core design principles of coarse-grained,
dynamic IFC systems.

>>>>

In this paper, we argued that when designing a coarse-grained IFC
system, it is better to start with a fully isolated, multi-task system
and work one's way back to the model of a single language equipped
with IFC.  We showed
how systems designed this way can be proved non-interferent
without needing to rely on details of the target language, and
we provided conditions on how to securely refine our formal semantics to
consider optimizations required in practice.  We connected our semantics
to two IFC implementations for JavaScript based on this formalism,
explained how our methodology improved an exiting IFC system for Haskell,
and proposed
an IFC system for C using hardware isolation.
By systematically applying ideas from IFC in operating systems to programming languages,
we hope to have elucidated some of the core design principles of coarse-grained,
dynamic IFC systems.

### 2015-01-07 paper/concrete.tex
reviewer 1 grammar/spelling

The operational semantics we have defined in the previous section
satisfy non-interference by design.
We achieve this general statement that works for a large class of
languages by having different tasks executing completely isolated from
each other, such that every task has its own state.
In some cases, this strong separation is desirable, or even necessary.
Languages like C provide direct access to memory locations without
mechanisms in the language to achieve a separation of the heap.
On the other hand, for other languages, this
strong isolation of tasks can be
undesirable, e.g., for performance reasons.
For instance, for the language |targetLangML|, our presentation so far
requires a separate heap per task, which is not very practical.
Instead, we would like to
more tightly couple the integration of the target and IFC
language by reusing existing infrastructure.  In the running example,
a concrete implementation might use a single global heap.
More precisely, instead of using a configuration of the form
$|iconf iS (fullconf id1 il1 tS1 ie1, fullconf id2 il2 tS2 ie2 ldots)|$
we would like a single global heap as in
$|oneheapiconf iS tS (oneheapfullconf id1 il1 ie1, oneheapfullconf id2 il2 ie2, ldots)|$

If the operational rules are adapted na\"ively to this new setting,
then non-interference can be violated: as we mentioned earlier,
shared mutable cells could result in violation of non-interference.
What we would like is a way of characterizing safe modifications to
the semantics which preserve non-interference.
The intention of our single heap implementation is to permit
efficient execution while \emph{conceptually maintaining isolation between
tasks} (by not allowing sharing of references between them).
This intuition of having a different (potentially more efficient)
concrete semantics that behave like the abstract semantics
can be formalized by the following definition:

@@

Only weak isomorphism is necessary for TINI. Intuitively, this is because
is not necessary to back-translate reduction sequences in $L'$ to
$L$; by the definition of TINI, we have both reduction sequences in $L$
by assumption.

@@

Unfortunately, an isomorphism is often too strong of a requirement.
To obtain an isomorphism with our single heap semantics, we need to mimic the
behavior of several heaps with a single actual heap.
The interesting cases are when we sandbox
an expression and when messages are sent and received.
The rule for sandboxing is
parametrized by the strategy |klone| (cf.\ Section~\ref{sec:retrofit}),
which defines what heap the new task
should execute with.  We have considered two choices:

@@

While this sounds plausible, it is worth noting that we are modifying the IFC language semantics,
which raises the question whether non-interference is preserved.
This question can be subtle: it is easy to remove a transition from
a language and invalidate TSNI.  Intuitively
if the restriction depends on secret data, then a public thread
can observe if some other task terminates or not, and by that obtain
information about the secret data that was used to restrict the
transition.
With this in mind, we require semantic rules to get restricted only
based on information observable by the task triggering them.
This ensures that non-interference is preserved, as the
restriction does not depend on confidential information.
Below, we give the formal definition of this condition for the
abstract IFC language |specLang alpha targetLang|.

@@

\begin{definition}[Restricted IFC language]
  \label{def:restricted}
  For a family of predicates $\mathcal P$ (one for every reduction
  rule), we call
  |restrictedLang alpha targetLang| a restricted IFC language
  if its definition is equivalent to the abstract language
  |specLang alpha targetLang|, with the following exception:
  The reduction rules are restricted
  by adding a predicate $P \in \mathcal P$ to the premise of
  all rule other than \textsc{I-noStep}.  Furthermore, the predicates $P$
  can depend only on the \textit{erased} configuration
  |erase il ic|, where |il| is the label of the first task
  in the task list and |ic| the full configuration.
\end{definition}

>>>>

The operational semantics we have defined in the previous section
satisfy non-interference by design.
We achieve this general statement that works for a large class of
languages by having different tasks executing completely isolated from
each other, such that every task has its own state.
In some cases, this strong separation is desirable, or even necessary.
Languages like C provide direct access to memory locations without
mechanisms in the language to achieve a separation of the heap.
On the other hand, for other languages, this
strong isolation of tasks can be
undesirable, e.g., for performance reasons.
For instance, for the language |targetLangML|, our presentation so far
requires a separate heap per task, which is not very practical.
Instead, we would like to
more tightly couple the integration of the target and IFC
languages by reusing existing infrastructure.  In the running example,
a concrete implementation might use a single global heap.
More precisely, instead of using a configuration of the form
$|iconf iS (fullconf id1 il1 tS1 ie1, fullconf id2 il2 tS2 ie2 ldots)|$
we would like a single global heap as in
$|oneheapiconf iS tS (oneheapfullconf id1 il1 ie1, oneheapfullconf id2 il2 ie2, ldots)|$

If the operational rules are adapted na\"ively to this new setting,
then non-interference can be violated: as we mentioned earlier,
shared mutable cells could result in violation of non-interference.
What we would like is a way of characterizing safe modifications to
the semantics which preserve non-interference.
The intention of our single heap implementation is to permit
efficient execution while \emph{conceptually maintaining isolation between
tasks} (by not allowing sharing of references between them).
This intuition of having a different (potentially more efficient)
concrete semantics that behaves like the abstract semantics
can be formalized by the following definition:

@@

Only weak isomorphism is necessary for TINI. Intuitively, this is because
it is not necessary to back-translate reduction sequences in $L'$ to
$L$; by the definition of TINI, we have both reduction sequences in $L$
by assumption.

@@

Unfortunately, an isomorphism is often too strong of a requirement.
To obtain an isomorphism with our single heap semantics, we need to mimic the
behavior of several heaps with a single actual heap.
The interesting cases are when we sandbox
an expression and when messages are sent and received.
The rule for sandboxing is
parametrized by the strategy |klone| (see Section~\ref{sec:retrofit}),
which defines what heap the new task
should execute with.  We have considered two choices:

@@

While this sounds plausible, it is worth noting that we are modifying the IFC language semantics,
which raises the question of whether non-interference is preserved.
This question can be subtle: it is easy to remove a transition from
a language and invalidate TSNI.  Intuitively
if the restriction depends on secret data, then a public thread
can observe if some other task terminates or not, and from that obtain
information about the secret data that was used to restrict the
transition.
With this in mind, we require semantic rules to get restricted only
based on information observable by the task triggering them.
This ensures that non-interference is preserved, as the
restriction does not depend on confidential information.
Below, we give the formal definition of this condition for the
abstract IFC language |specLang alpha targetLang|.

@@

\begin{definition}[Restricted IFC language]
  \label{def:restricted}
  For a family of predicates $\mathcal P$ (one for every reduction
  rule), we call
  |restrictedLang alpha targetLang| a restricted IFC language
  if its definition is equivalent to the abstract language
  |specLang alpha targetLang|, with the following exception:
  The reduction rules are restricted
  by adding a predicate $P \in \mathcal P$ to the premise of
  all rules other than \textsc{I-noStep}.  Furthermore, the predicates $P$
  can depend only on the \textit{erased} configuration
  |erase il ic|, where |il| is the label of the first task
  in the task list and |ic| the full configuration.
\end{definition}

### 2015-01-07 paper/formal.tex
reviewer 1 grammar/spelling

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Our language |specLang alpha (targetLang nop)| fulfills
this definition as |(ifc C, .->, erasef il)|, where
$|ifc C| = |iS| \times \operatorname{List}(|it|)$.  The set of terminal conditions
$|ifc V|$ is $|iS| \times |it|_V$, where $|it|_V \subset |it|$ is the
type for tasks whose expressions have been reduced to
values.\footnote{
  Here, we abuse notation by describing types for configuration parts using the
  same metavariables as the ``instance'' of the type, e.g., |it| for the type of
  task.
}
The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
containing |bullet|, and Fig.~\ref{fig:erasure} gives the precise definition for
our erasure function |erasef il|.
%
Essentially, a task and its corresponding message queue is completely erased from the task
list if its label does not flow to the attacker observation level |il|.
Otherwise, we apply the erasure function homomorphically and remove any message
from the task's message queue that are more sensitive than |il|.
%}

@@

Given an information flow control language, we can now define non-interference.
Intuitively, we want to make statements about the attacker's observational
power at some security level |l|.  This is done by defining an equivalence
relation called |l|-equivalence on configurations: an attacker should
not be able to distinguish two configuration that are |l|-equivalent.
%
Since our erasure function captures what an attacker can or cannot observe, we simply define this
equivalence as the syntactic-equivalence of erased configurations~\cite{stefan:addressing-covert}.
%
\begin{definition}[|l|-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    |memberf (c, c') C| are considered $l$-equivalent, written as |c ~= c'|,
    if |erase l c = erase l c'|.
\end{definition}
%

@@

However, even non-adversarial schedulers are not always safe.
Consider, for example, the sequential scheduling policy |seqf| given in
Fig.~\ref{fig:scheduler}.
%
It is easy to show that |specLang seqf targetLang| does not satisfy
TSNI:
%
consider a target language similar to |targetLangML| with an
additional expression terminal |diverge| that denotes a divergent computation,
i.e., |diverge| always reduces to |diverge| and a simple label lattice |{pub,
sec}| such that |canFlowTo2 pub sec|, but |cantFlowTo2 sec pub|.
Consider the following two configurations in this language:
\begin{code}
ic1 = iS ; fullconf 1 sec tS1 (IT(if false then diverge else true)),  fullconf 2 pub tS2 ie
ic2 = iS ; fullconf 1 sec tS1 (IT(if true then diverge else true)),   fullconf 2 pub tS2 ie
\end{code}
These two configurations are |pub|-equivalent, but |ic1| will reduce
(in two steps)
to |ic1 = iS ; fullconf 2 pub tS1 (IT true)|, whereas |ic2| will not make
any progress.
%
Suppose that |ie| is a computation that writes to a |pub| channel,\footnote{
Though we do not model labeled channels, extending the calculus with such a
feature is straight forward, see Section~\ref{sec:extensions}.}
then the |sec| task's decision to diverge or not is directly leaked to a
public entity.

>>>>

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Our language |specLang alpha (targetLang nop)| fulfills
this definition as |(ifc C, .->, erasef il)|, where
$|ifc C| = |iS| \times \operatorname{List}(|it|)$.  The set of terminal conditions
$|ifc V|$ is $|iS| \times |it|_V$, where $|it|_V \subset |it|$ is the
type for tasks whose expressions have been reduced to
values.\footnote{
  Here, we abuse notation by describing types for configuration parts using the
  same metavariables as the ``instance'' of the type, e.g., |it| for the type of
  task.
}
The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
containing |bullet|, and Fig.~\ref{fig:erasure} gives the precise definition for
our erasure function |erasef il|.
%
Essentially, a task and its corresponding message queue is completely erased from the task
list if its label does not flow to the attacker observation level |il|.
Otherwise, we apply the erasure function homomorphically and remove any messages
from the task's message queue that are more sensitive than |il|.
%}

@@

Given an information flow control language, we can now define non-interference.
Intuitively, we want to make statements about the attacker's observational
power at some security level |l|.  This is done by defining an equivalence
relation called |l|-equivalence on configurations: an attacker should
not be able to distinguish two configurations that are |l|-equivalent.
%
Since our erasure function captures what an attacker can or cannot observe, we simply define this
equivalence as the syntactic-equivalence of erased configurations~\cite{stefan:addressing-covert}.
%
\begin{definition}[|l|-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    |memberf (c, c') C| are considered $l$-equivalent, written as |c ~= c'|,
    if |erase l c = erase l c'|.
\end{definition}
%

@@

However, even non-adversarial schedulers are not always safe.
Consider, for example, the sequential scheduling policy |seqf| given in
Fig.~\ref{fig:scheduler}.
%
It is easy to show that |specLang seqf targetLang| does not satisfy
TSNI:
%
consider a target language similar to |targetLangML| with an
additional expression terminal |diverge| that denotes a divergent computation,
i.e., |diverge| always reduces to |diverge| and a simple label lattice |{pub,
sec}| such that |canFlowTo2 pub sec|, but |cantFlowTo2 sec pub|.
Consider the following two configurations in this language:
\begin{code}
ic1 = iS ; fullconf 1 sec tS1 (IT(if false then diverge else true)),  fullconf 2 pub tS2 ie
ic2 = iS ; fullconf 1 sec tS1 (IT(if true then diverge else true)),   fullconf 2 pub tS2 ie
\end{code}
These two configurations are |pub|-equivalent, but |ic1| will reduce
(in two steps)
to |ic1 = iS ; fullconf 2 pub tS1 (IT true)|, whereas |ic2| will not make
any progress.
%
Suppose that |ie| is a computation that writes to a |pub| channel,\footnote{
Though we do not model labeled channels, extending the calculus with such a
feature is straightforward, see Section~\ref{sec:extensions}.}
then the |sec| task's decision to diverge or not is directly leaked to a
public entity.

### 2015-01-07 paper/intro.tex
reviewer 1 grammar/spelling

%In the alternative \textit{coarse-grained} approach to IFC,
The Operating Systems community has tackled this challenge (e.g.,
in~\cite{Zeldovich:2006}) by taking a \textit{coarse-grained} approach
to IFC: dividing an application into coarse computational units,
each with a single label dictating its security policy, and only
monitoring communication between them.
%Only communication between isolated computational units must be tracked.
%A recent system named COWL~\cite{swapi} adds IFC to the
%browser by identifying \emph{web workers} as an existing computational
%unit.  Communication between workers is mediated using
%IFC to ensure non-interference, preventing sensitive workers from
%influencing the computation of less sensitive workers.
This coarse-grained approach provides a number of advantages when
compared to the fine-grained approaches typically employed by language-based systems.
First, adding IFC does not require intrusive changes to an
existing programming language, thereby also allowing
the reuse of existing programs.  Second, it has a small
runtime overhead because checks need only
be performed at isolation boundaries
instead of (almost) every program instruction~(e.g.,~\cite{JSFlow}).
%, compared to fine-grained
%systems were the runtime overhead can be impractical~\cite{JSFlow}.
Finally, by associating
a single security label with the entire computational unit simplifies
understanding and reasoning about the security guarantees of the
system, without reasoning about most of the
technical details of the semantics of the underlying programming language.

In this paper, we present a framework which brings coarse-grained IFC
ideas into a language-based setting:
%take coarse-grained labeling~\cite{Zeldovich:2006,
%lio} to its logical extreme:
an information flow control system should
be thought of as multiple instances of completely isolated language
runtimes or \emph{tasks}, with information flow control applied to
inter-task communication.  We describe a formal system in which an IFC
system can be designed once and then applied to any programming language
which has control over external effects (e.g., JavaScript or C with
access to hardware privilege separation).  We formalize this system
using an approach by
Matthews and Findler~\cite{Matthews:2007:OSM:1190216.1190220} for combining
operational semantics and prove non-interference guarantees
that are independent of the choice of an specific target language.

@@

Our contributions can be summarized as follows:
\begin{itemize}
  \item We give formal semantics for a core coarse-grained
  dynamic information flow control language free of non-IFC constructs.
  We then show how a large class of target languages can be combined
  with this IFC language and prove that the result provides
  non-interference. (Sections~\ref{sec:retrofit} and \ref{sec:formal})
  \item We provide a proof technique to show the non-interference
  of a concrete semantics for a potentially optimized IFC language
  by means of an isomorphism and show a class of restrictions on
  the IFC language that preserves non-interference. (Sections~\ref{sec:concrete})
  \item We implemented an IFC system based on these semantics
  for Node.js, and we connect our formalism to another implementation
  based on this work for client-side JavaScript~\cite{swapi}.
  Furthermore, we outline an implementation for the C programming
  language and describe improvements to the Haskell LIO system that
  resulted from this framework.
  (Section~\ref{sec:real})
%  \item We show how to extend the Matthews-Findler method from just
%  languages that are not simply expressions evaluating to values,
%  but may be collections of threads executing nondeterministically.
%  \item We describe ways to enrich the core IFC language with
%  more advanced concepts such as labeled values, labeled references, or a
%  notion of clearance. (Section~\ref{sec:extensions})
\end{itemize}

>>>>

%In the alternative \textit{coarse-grained} approach to IFC,
The Operating Systems community has tackled this challenge (e.g.,
in~\cite{Zeldovich:2006}) by taking a \textit{coarse-grained} approach
to IFC: dividing an application into coarse computational units,
each with a single label dictating its security policy, and only
monitoring communication between them.
%Only communication between isolated computational units must be tracked.
%A recent system named COWL~\cite{swapi} adds IFC to the
%browser by identifying \emph{web workers} as an existing computational
%unit.  Communication between workers is mediated using
%IFC to ensure non-interference, preventing sensitive workers from
%influencing the computation of less sensitive workers.
This coarse-grained approach provides a number of advantages when
compared to the fine-grained approaches typically employed by language-based systems.
First, adding IFC does not require intrusive changes to an
existing programming language, thereby also allowing
the reuse of existing programs.  Second, it has a small
runtime overhead because checks need only
be performed at isolation boundaries
instead of (almost) every program instruction~(e.g.,~\cite{JSFlow}).
%, compared to fine-grained
%systems were the runtime overhead can be impractical~\cite{JSFlow}.
Finally, associating
a single security label with the entire computational unit simplifies
understanding and reasoning about the security guarantees of the
system, without reasoning about most of the
technical details of the semantics of the underlying programming language.

In this paper, we present a framework which brings coarse-grained IFC
ideas into a language-based setting:
%take coarse-grained labeling~\cite{Zeldovich:2006,
%lio} to its logical extreme:
an information flow control system should
be thought of as multiple instances of completely isolated language
runtimes or \emph{tasks}, with information flow control applied to
inter-task communication.  We describe a formal system in which an IFC
system can be designed once and then applied to any programming language
which has control over external effects (e.g., JavaScript or C with
access to hardware privilege separation).  We formalize this system
using an approach by
Matthews and Findler~\cite{Matthews:2007:OSM:1190216.1190220} for combining
operational semantics and prove non-interference guarantees
that are independent of the choice of a specific target language.

@@

Our contributions can be summarized as follows:
\begin{itemize}
  \item We give formal semantics for a core coarse-grained
  dynamic information flow control language free of non-IFC constructs.
  We then show how a large class of target languages can be combined
  with this IFC language and prove that the result provides
  non-interference. (Sections~\ref{sec:retrofit} and \ref{sec:formal})
  \item We provide a proof technique to show the non-interference
  of a concrete semantics for a potentially optimized IFC language
  by means of an isomorphism and show a class of restrictions on
  the IFC language that preserves non-interference. (Section~\ref{sec:concrete})
  \item We have implemented an IFC system based on these semantics
  for Node.js, and we connect our formalism to another implementation
  based on this work for client-side JavaScript~\cite{swapi}.
  Furthermore, we outline an implementation for the C programming
  language and describe improvements to the Haskell LIO system that
  resulted from this framework.
  (Section~\ref{sec:real})
%  \item We show how to extend the Matthews-Findler method from just
%  languages that are not simply expressions evaluating to values,
%  but may be collections of threads executing nondeterministically.
%  \item We describe ways to enrich the core IFC language with
%  more advanced concepts such as labeled values, labeled references, or a
%  notion of clearance. (Section~\ref{sec:extensions})
\end{itemize}

### 2015-01-07 paper/real.tex
reviewer 1 grammar/spelling

Luckly, this issue is not unique to our work---browser layout engines
also rely on isolating code executing in separate iframes (e.g., according to the
same-origin policy).
%
Since creating an OS thread for each iframe is expensive, both
the V8 and SpiderMonkey JavaScript engines provide a means for running
JavaScript code in isolation in a single OS thread,
on disjoint sub-heaps.
%
In V8, this unit of isolation is called a \emph{context}; in
SpiderMonkey, it is called a \emph{compartment}.
%
(We will use these terms interchangably.)
%
Each context is associated with a global object, which, by
default, implements the JavaScript standard library (e.g.,
\verb|Object|, \verb|Array|, etc.).
%
Naturally, we adopt contexts to implement our notion of tasks.

@@

\begin{figure}[t]
\centerline{\includegraphics[width=0.7\columnwidth]{figs/node}}
\caption{\label{fig:node}
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced (right).}
\end{figure}
%
\paragraph{Server-side IFC for Node.js:}
We have implemented |specLangJS seqf| for Node.js in the form of a
library, without modifying Node.js or the V8 JavaScript engine.
%
Our implementation\footnote{Available at \codelink{}.} provides a
library for creating new tasks, i.e., contexts whose global object
only contains the standard JavaScript library and our IFC primitives
(e.g., |send| and |sandbox|).
%
When mapped to our formal treatement, |sandbox| is defined with |ap
klone tS = tS0|, where |tS0| is the global object corresponding to the
standard JavaScript library and our IFC primitives.
%
%These tasks can communicate and create new tasks, in turn.
%
These IFC operations are mediated by the trusted library code (executing
as the main Node.js context), which tracks the state (current label, messages,
etc.) of each task.  An example for |send|/|recv| is shown in
Fig.~\ref{fig:node}.
%While V8 provides a means for sharing any object between contexts (used
%by same-origin contexts in Blink),
We remark that our system conservatively restricts
the kinds of messages that can be exchanged, via |send| (and |sandbox|),
to string values.
%
(We provide a convenience library which marshalls JSON objects to/from strings.)
%
In our formalization, this amounts to restricting the IFC language rule
for |send| in the following way:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%

@@

Furthermore, COWL repurposes existing contexts (e.g., iframes and
pages) as IFC tasks, only imposing additional constraints on how they
communicate.
%
As for Node.js, at its core, the global object of a COWL task
should only contain the standard JavaScript libraries and
\texttt{postMessage}, whose semantics are modeled by our
\textsc{JS-send} rule.
%
However, existing contexts have objects such as the DOM, which
demands COWL to restrict a task's external effects.
%
To this end, COWL mediates any communication (even via the DOM) at
the context boundary. %by COWL.

Simply disallowing all the external effects is overly-restricting for
real-world applications (e.g., pages typically load images, perform
network requests, etc.).
%
In this light, COWL allows safe network communication by associating an
implicit label with remote hosts (a host's label corresponds to
its origin).
%
In turn, when a task perform a request, the COWL's IFC monitor
ensures that the task label can flow to the remote origin label.
%
While the external effects of COWL can be formally modeled, we do not
model them in our formalism, %more general framework,
since, like for the
Node.js case, they are specific to this system.
%
%Indeed, even the labeled HTTP client in  Node.js and COWL differ, even
%though they're both JavaScript systems, simply because of the
%differing environments.

@@

%Indeed, by rephrasing LIO in terms of our framework, we simplified
%LIO's treatment of exceptions.
%
Different from our proposal, LIO originally associated labels with exceptions, in a
similar style to fine-grained
systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
%
In addition to being overly complex, the interaction of exceptions
with clearance (which sets an upper bound on the floating label, see
Section~\ref{sec:clearance}) was incorrect: the clearance
was restored to the clearance at point of the catch.
%
Furthermore, pure exceptions (e.g., divide by zero) always percolated to
trusted code, effectively allowing for denial of service attacks.
%
The insights gained when viewing coarse-grained IFC as presented in this
paper led to a much cleaner, simpler treatment of exceptions in LIO,
which has now been adapted by LIO.
%By using isolated tasks, and thus treating the current label (and
%clearance) as global, the underlying Haskell exception system can be
%used directly: exceptional control flow does not affect IFC.

@@

In this setting, the combined language of Section~\ref{sec:retrofit}
can be interpreted in the following way: calling from the target
language to the IFC language corresponds to invoking a system call.
%
Creating a new task with the |sandbox| system call corresponds to
\emph{forking} a process.  Using page tables, we can ensure that
there will be no shared memory
(effectively
defining |ap klone tS
= tS0|, where |tS0| is the set of pages necessary to bootstrap a
lightweight process.)
%
Similarly, control over page tables and protection bits allows us to
define a |send| syscall that copies pages to our
(trusted) runtime queue; and, correspondingly, a |recv| that copies
the pages from the runtime queue to the (untrusted) receiver.
%
Since C is not memory safe, conditions on these system calls are
meaningless.
%
We leave the implementation of this IFC system for C as future work.

>>>>

Luckily, this issue is not unique to our work---browser layout engines
also rely on isolating code executing in separate iframes (e.g., according to the
same-origin policy).
%
Since creating an OS thread for each iframe is expensive, both
the V8 and SpiderMonkey JavaScript engines provide a means for running
JavaScript code in isolation in a single OS thread,
on disjoint sub-heaps.
%
In V8, this unit of isolation is called a \emph{context}; in
SpiderMonkey, it is called a \emph{compartment}.
%
(We will use these terms interchangeably.)
%
Each context is associated with a global object, which, by
default, implements the JavaScript standard library (e.g.,
\verb|Object|, \verb|Array|, etc.).
%
Naturally, we adopt contexts to implement our notion of tasks.

@@

\begin{figure}[t]
\centerline{\includegraphics[width=0.7\columnwidth]{figs/node}}
\caption{\label{fig:node}
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced (right).}
\end{figure}
%
\paragraph{Server-side IFC for Node.js:}
We have implemented |specLangJS seqf| for Node.js in the form of a
library, without modifying Node.js or the V8 JavaScript engine.
%
Our implementation\footnote{Available at \codelink{}.} provides a
library for creating new tasks, i.e., contexts whose global object
only contains the standard JavaScript library and our IFC primitives
(e.g., |send| and |sandbox|).
%
When mapped to our formal treatment, |sandbox| is defined with |ap
klone tS = tS0|, where |tS0| is the global object corresponding to the
standard JavaScript library and our IFC primitives.
%
%These tasks can communicate and create new tasks, in turn.
%
These IFC operations are mediated by the trusted library code (executing
as the main Node.js context), which tracks the state (current label, messages,
etc.) of each task.  An example for |send|/|recv| is shown in
Fig.~\ref{fig:node}.
%While V8 provides a means for sharing any object between contexts (used
%by same-origin contexts in Blink),
We remark that our system conservatively restricts
the kinds of messages that can be exchanged, via |send| (and |sandbox|),
to string values.
%
(We provide a convenience library which marshalls JSON objects to/from strings.)
%
In our formalization, this amounts to restricting the IFC language rule
for |send| in the following way:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%

@@

Furthermore, COWL repurposes existing contexts (e.g., iframes and
pages) as IFC tasks, only imposing additional constraints on how they
communicate.
%
As with Node.js, at its core, the global object of a COWL task
should only contain the standard JavaScript libraries and
\texttt{postMessage}, whose semantics are modeled by our
\textsc{JS-send} rule.
%
However, existing contexts have objects such as the DOM, which
demands COWL to restrict a task's external effects.
%
To this end, COWL mediates any communication (even via the DOM) at
the context boundary. %by COWL.

Simply disallowing all the external effects is overly-restricting for
real-world applications (e.g., pages typically load images, perform
network requests, etc.).
%
In this light, COWL allows safe network communication by associating an
implicit label with remote hosts (a host's label corresponds to
its origin).
%
In turn, when a task perform a request, COWL's IFC monitor
ensures that the task label can flow to the remote origin label.
%
While the external effects of COWL can be formally modeled, we do not
model them in our formalism, %more general framework,
since, like for the
Node.js case, they are specific to this system.
%
%Indeed, even the labeled HTTP client in  Node.js and COWL differ, even
%though they're both JavaScript systems, simply because of the
%differing environments.

@@

%Indeed, by rephrasing LIO in terms of our framework, we simplified
%LIO's treatment of exceptions.
%
Unlike our proposal, LIO originally associated labels with exceptions, in a
similar style to fine-grained
systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
%
In addition to being overly complex, the interaction of exceptions
with clearance (which sets an upper bound on the floating label, see
Section~\ref{sec:clearance}) was incorrect: the clearance
was restored to the clearance at point of the catch.
%
Furthermore, pure exceptions (e.g., divide by zero) always percolated to
trusted code, effectively allowing for denial of service attacks.
%
The insights gained when viewing coarse-grained IFC as presented in this
paper led to a much cleaner, simpler treatment of exceptions in LIO,
which has now been adopted by LIO.
%By using isolated tasks, and thus treating the current label (and
%clearance) as global, the underlying Haskell exception system can be
%used directly: exceptional control flow does not affect IFC.

@@

In this setting, the combined language of Section~\ref{sec:retrofit}
can be interpreted in the following way: calling from the target
language to the IFC language corresponds to invoking a system call.
%
Creating a new task with the |sandbox| system call corresponds to
\emph{forking} a process.  Using page tables, we can ensure that
there will be no shared memory
(effectively
defining |ap klone tS
= tS0|, where |tS0| is the set of pages necessary to bootstrap a
lightweight process).
%
Similarly, control over page tables and protection bits allows us to
define a |send| syscall that copies pages to our
(trusted) runtime queue; and, correspondingly, a |recv| that copies
the pages from the runtime queue to the (untrusted) receiver.
%
Since C is not memory safe, conditions on these system calls are
meaningless.
%
We leave the implementation of this IFC system for C as future work.
